\textit{A young boy with a tree made of trees}: \\ Domain Adaptation of an LSTM-based Image Caption Generation Model

### 2023-01-05 paper/paper.tex
Adding tables

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{1cm}|p{4.5cm}|}
\hline \bf Image & \bf Best model (\% responses) \\ \hline
40416 & original (83.3\%)  \\
39158 & original (50\%)  \\
25053 & original (83.3\%)  \\
30620 & 100\_1.0 (66.7\%)  \\
32397 & 100\_0.2 (66.7\%) \\
38937 & original (50\%) \\
39005 & 100\_0.1 (33.3\%) or 100\_0.15 (33.3\%) or 100\_0.2 (33.3\%) \\
40120 & original (66.7\%) \\
23588 & 100\_1.0 (83.3\%)  \\
39472 & 100\_0.1 (66.7\%)  \\
30138 & original (50\%)  \\
40202 & 100\_0.1 (83.3\%)  \\
35895 & original (66.7\%)  \\
32663 & 100\_0.2 (83.3\%)   \\
30705 & original (83.3\%) \\
38081 & 100\_0.15 (66.7\%) \\
31571 & original (100\%) \\
35858 & original (66.7\%) \\
37836 & 100\_0.1 (33.3\%) or 100\_0.15 (33.3\%) \\
39239 & 100\_0.15, 100\_0.2, and 100\_1.0 (50\%)\footnote{These models generated identical captions.} \\
\hline
\end{tabular}
\end{center}
\caption{\label{filtered-table} Best captions per image in the filtered imageCLEF test set. }
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3.5cm}|}
\hline \bf Image & \bf Best model (\% responses) \\ \hline
2116444946\_ 1f5d1fe5d1 & original (100\%)  \\
2316097768\_ ef662f444b & original (100\%)  \\
2439384468\_ 58934deab6 & original (66.7\%)  \\
2112921744\_ 92bf706805 & 100\_0.2 (50\%)  \\
2392460773\_ 2aa01eb340 & original (100\%) \\
2434006663\_ 207a284cec & original (100\%) \\
2308256827\_ 3c0a7d514d & original (100\%) \\
2111360187\_ d2505437b7 & original (66.7\%) \\
2271671533\_ 7538ccd556 & original (66.7\%)  \\
2328616978\_ fb21be2b87 & original (100\%)  \\
2456907314\_ 49bc4591c4 & original (66.7\%)  \\
2229179070\_ dc8ea8582e & 100\_0.1 (100\%)  \\
2279980395\_ 989d48ae72 & 100\_0.1 (88.3\%)  \\
2393971707\_ bce01ae754 & original (83.3\%)   \\
211277478\_ 7d43aaee09 & 100\_0.1 (50\%) \\
2337919839\_ df83827fa0 & original (83.3\%) \\
2447035752\_ 415f4bb152 & original (50\%) \\
23445819\_ 3a458716c1 & 100\_0.2 (66.7\%) \\
2448210587\_ 9fe7ea5f42 & original (33.3\%) \\
2445654384\_ 4ee3e486e1 & 100\_0.1 (50\%) or 100\_0.2 (50\%)\\
\hline
\end{tabular}
\end{center}
\caption{\label{flickr-table} Best captions per image in the Flickr8k test set. }
\end{table}
